---
title: "stringops"
author: Robert Schnitman
date: "8/8/2020"
output:
  md_document:
    variant: markdown_github
---

# `stringops`: Tools for processing strings in R

When creating syntax, one has to ask themselves about the naming scheme: should I make the functions short for typing efficiency, or long for increased readability? Ruby has the former benefit, but sometimes the methods can be difficult to remember (e.g. is it `len` or `length`? Is it `swapcase` or `swap_case`?), as there isn't a consistent naming scheme--however, some functions have synonyms to help those from other programming languages learn Ruby faster (e.g. `reduce` and `inject` do the same thing). On the other hand, the `stringr` library has a consisent naming scheme for its functions, but does not have synonyms, so you are forced to learn the `stringr` way. Thirdly, and perhaps tagentially, R does not have concatenation operator (only functions) like in Ruby and BASIC, which is odd, as many situations require concatenation; so using the `paste/paste0()` functions can make code less readable. As such, I am introducing a new package to take these considerations into account: `stringops`, a work-in-progress library consisting of tools for processing strings in R.

What this package brings are (1) a consistent naming-scheme for functions, (2) synonyms for said functions, and (3) a concatenation operator. The first item benefits users of all skill levels, as it makes certain functions easier to remember while making use of RStudio's predictive text. The second item is useful when one tires of typing `string_cull()`, for example, and wishes to use a shorthand to simplify the code (in this case, the shorthand would be `cull()`). The third item's benefit is more readable code by avoiding the function syntax of `paste/paste0()`. Ultimately, these items will hopefully make processing strings in R more fun for the user!

The following sections detail the installation procedure and a sample of functions from this package.

# Installation
This package currently is only available on GitHub--there are no plans to submit this package to CRAN at this time. As such, please use the `devtools` library to install `stringops`.

```{r, eval = FALSE}
# install.packages('devtools')

devtools::install_github('robertschnitman/stringops')
```

```{r}
library(stringops)
```


# `%&%`

As inspired by [AutoIt](https://www.autoitscript.com/autoit3/docs/intro/lang_operators.htm), the `%&%` (concatenation) operator joins two strings together. This operator facilitates readable code by avoiding the function syntax of the `paste/paste0()`.

```{r}
'a' %&% 'b'

"Car: " %&% rownames(mtcars)
```

# `string_cull`()

As inspired by Ruby, the function `string_cull()` culls (or extracts) pattern matches from strings--if a pattern is not found, then `NA` is returned. The synonyms for this function are `s_cull()`, `cull()`, `string_extract()`, `s_extract()`, and `extract()`.

```{r}
# extract beginning "M" from each element.
string_cull(rownames(mtcars), '^M')
```

```{r}
# extract elements in full that begin with "M".
string_cull(rownames(mtcars), "^M.*")
```

# `string_find()`

The function "string_find" acts similar to `grep(string, x, value = TRUE)`: it subsets a vector to found pattern matches, returning the full element. The synonyms for this function are `s_find()`, and `find()`.

```{r}
string_find(rownames(mtcars), '^M')
```